Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2020-04-30 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

% The paper headers
\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, April~2020}%
{Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

\IEEEPARstart{L}{ack} of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}. Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; specifically, grid extension are the standard in urban areas~\cite{IEAweo2018}.

>>>>

% The paper headers
\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, April~2020}%
{Trindade and Cordeiro: Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

\IEEEPARstart{L}{ack} of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in $2017$~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}. 
Decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems are the lowest-cost solution for three-quarters of the additional connections needed to provide universal electricity~\cite{Hussein2012}; specifically, grid extension are the standard in urban areas~\cite{IEAweo2018}.
